### 2018-01-28 README.Rmd
update readme

Download the files to your desktop, open `modelextinctionideas.Rproj` in RStudio, install the `modelextinctionideas` package (CTRL+SHIFT+B) then open `analysis/paper/paper.Rmd` and knit the Rmd to run the code and generate the results and plots found in the paper.

>>>>

In RStudio, open `modelextinctionideas.Rproj` install the `modelextinctionideas` package (press CTRL+SHIFT+B or click Build -> Install and restart) then open `analysis/paper/paper.Rmd` and knit the Rmd to run the code and generate the results and plots found in the paper.
